---
title: "Rendering gallery"
description: "Live examples of backgammonboard rendering positions, cube states, match context, perspective, and movement overlays."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.asp = 0.72,
  dpi = 96
)

library(backgammonboard)

fixture_file <- system.file(
  "fixtures",
  "xgid-factual-fixtures.csv",
  package = "backgammonboard"
)
fixtures <- utils::read.csv(fixture_file, stringsAsFactors = FALSE)

xgid_for <- function(id) {
  value <- fixtures$xgid[match(id, fixtures$fixture_id)]
  if (length(value) != 1L || is.na(value)) {
    stop("Unknown gallery fixture: ", id, call. = FALSE)
  }
  value
}

bs_colors <- board_colors("bs")
bs_style <- board_style("bs")
```

This gallery is generated from the package itself. The positions come from the factual fixtures shipped with `backgammonboard`, and the figures are rendered by the installed package during the pkgdown build. When the renderer changes, rebuilding the documentation regenerates these examples from the current code.

## Opening position

A normal position with dice on the board.

```{r opening, fig.cap="Opening position rendered with the Backgammon Simplified preset."}
ggboard(
  xgid_for("opening_white_roll"),
  colors = bs_colors,
  style = bs_style
)
```

## Checker on the bar

Bar occupancy remains part of factual position state and follows the selected display perspective.

```{r bar, fig.cap="Position with a checker on the bar."}
ggboard(
  xgid_for("white_bar"),
  colors = bs_colors,
  style = bs_style,
  decision = "none"
)
```

## Borne-off checkers

Borne-off counts are rendered alongside the playing surface without changing point occupancy.

```{r borne-off, fig.cap="Position with borne-off checkers."}
ggboard(
  xgid_for("borne_off"),
  colors = bs_colors,
  style = bs_style,
  decision = "none"
)
```

## Owned doubling cube

Owned cubes remain on their factual owner's side.

```{r owned-cube, fig.cap="Position with a Black-owned doubling cube."}
ggboard(
  xgid_for("black_owned_cube"),
  colors = bs_colors,
  style = bs_style,
  decision = "none"
)
```

## Offered doubling cube

Cube questions are explicit display decisions. An XGID carrying a pending double can be rendered as a take/pass decision.

```{r offered-cube, fig.cap="Pending double rendered as a take/pass decision."}
ggboard(
  xgid_for("offer_to_black"),
  decision = "take_pass",
  colors = bs_colors,
  style = bs_style
)
```

## Match score and Crawford state

Match metadata can be displayed in raw and away-score form.

```{r crawford, fig.cap="Crawford-game match display with both score formats."}
ggboard(
  xgid_for("crawford"),
  decision = "none",
  score_format = "both",
  colors = bs_colors,
  style = bs_style
)
```

## High cube value

The package supports factual cube values through its documented release boundary.

```{r cube-64, fig.cap="Owned 64-cube rendered from a release fixture."}
ggboard(
  xgid_for("cube_64"),
  decision = "none",
  colors = bs_colors,
  style = bs_style
)
```

## Perspective and mirroring

Perspective controls which factual player is shown near the viewer. Horizontal mirroring is independent, and `light_player = "near_player"` can keep the near player on the light visual palette.

```{r perspective, fig.cap="Asymmetric position with changed perspective, horizontal mirroring, and near-player light palette."}
ggboard(
  xgid_for("asymmetric_white_roll"),
  perspective = "player_0",
  mirror_horizontal = TRUE,
  light_player = "near_player",
  colors = bs_colors,
  style = bs_style
)
```

## Structured movement overlay

Movement overlays use ordered atomic movements. The renderer visualizes the supplied movement geometry; it does not certify complete-play legality or evaluate strategy.

```{r movement, eval=FALSE}
moves <- board_moves(
  from = c(13, 6),
  to = c(8, 5),
  die = c(5, 1),
  label = c("first", "second")
)

ggboard(
  xgid_for("opening_white_roll"),
  moves = moves,
  colors = bs_colors,
  style = bs_style
)
```

## GNUID input

Complete GNUIDs use the same public `ggboard()` entry point when `backgammoncalculator` 0.2.0 or later is installed.

```{r gnuid, eval=FALSE}
gnuid <- "4HPwATDgc/ABMA:8IhuACAACAAE"
ggboard(gnuid)
```

## Compose and export

`ggboard()` returns an ordinary `ggplot`, so standard `ggplot2` composition and export remain available.

```{r compose, eval=FALSE}
p <- ggboard(xgid_for("opening_white_roll"))

p + ggplot2::labs(title = "Backgammon position")

ggplot2::ggsave(
  filename = "backgammon-position.png",
  plot = p,
  width = 12,
  height = 7,
  dpi = 200
)
```
